---
title: "Validator quickstart guide"
author: "Vignette Author"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Quickstart guide}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

This is a super-dirty guide to the `validator` package. This package provides
tools to do repeated cross-validation.

The package currently resides only on GitHub and should be installed with devtools
```{r, eval=F}
devtools::install_github("3inar/validator", build_vignettes=T)
```

# Usage example
First, define an experiment function. This function should take the two arguments
`test_index` and `train_index`. It should return a test statistic and a train statistic by use of the `return_cv` function.
```{r}
library(datasets)
data(mtcars)

experiment <- function(test_index, train_index) {
  model <- lm(mpg~wt, data=mtcars, subset=train_index)
  
  test_mse <- mean((predict(model, mtcars[test_index, ]) - 
                                   mtcars[test_index, ]$mpg)^2)
  train_mse <- mean((predict(model) - mtcars[train_index, ]$mpg)^2)

  return_cv(test_mse, train_mse)
}
```

With the experiment code set up, we can use `repeat_cv` to run our repeated cross-validation:
```{r}
library(validator)

repetitions <- 500
k <- 5
n <- nrow(mtcars)

results <- repeat_cv(experiment, n, repetitions, k)

# results from the two first cross-validations
head(results, 2)
```

Let's see how our model does under resampling:
```{r}
library(plyr)

teststats <- laply(results, function(x) { x$test })
trainstats <- laply(results, function(x) { x$train })

boxplot(cbind(test=rowMeans(teststats), train=rowMeans(trainstats)))
```

# Conclusion
That's really all there is to it: make a function that takes test/train index, 
make sure to return a test and a train statistic.
